My title

### 2024-03-15 paper/paper.qmd
update

## Analyzing Voter Preferences Across Demographics

The analysis reveals critical insights into how education, age, race influence voting behavior. Contrary to conventional wisdom and past electoral analyses, our findings indicate a divergent pattern in voting behavior among different educational groups. The shift in party allegiance among non-college white voters from Democrats to Republicans and the nuanced preferences of voters with 'Some college' and 'Postgrad' education levels challenge the stereotypical narratives that educational attainment leads to an increase in support for the Democrats. This group, especially highly educated 'Postgrad' group being the second highest supporters suggest a reevaluation of Democrats' strategies to appeal to educated voters concerned with economic policies and national security. However, according to our data, the Republicans fail to attract voters as highest proportion of support among the four educational groups remain under 40 percent.

@@

From @fig-distribution-by-state, we can observe that Trump leads in mid-west of America, Montana (MT), Wyoming (WY), Mississippi (MS), Maine (ME), Missouri (MO), Kentucky (KY), and Utah (UT). Even the competing states like Louisiana (LA), New Mexico (NM), Tennessee (TN) are also mid-west part of the country, which are rural areas with low population density. This is correctly estimated since in the real world as Trump won in these states: MT, WY, MS, MA, MI, KY, UT. He also won in LA and TN, which we considered were competing states. We can go more in depth of this study with the benefit of hindsight. We estimated that the biggest victory for Trump would be Montana (MT) with just below 70%. In reality, he won by 59.6%, which is lower than we thought but still sit within our error values. The next state with the highest proportion of support for Trump was Wyoming (WY) from our model with 65%, which is close to the election poll result of 69%. We were very successful with Mississippi (MS) with an estimation of 57% and the poll result of 57.5%. Maine (ME) was another very close estimate with 52% and the poll result of 53.1%. 56.8% voted for Trump in Missouri (MO), which was slightly higher than our estimation of 51%. We estimated that only 26% of voters in Hawaii (HI) would vote for Trump with error margins of +-10%, which matched 34.3% for Trump in the election. 41.9% for Trump in Colorado (CO) lie within our estimate of 37% with +-5% margins.

@@

We were able to estimate the winning of states with some success

@@

Weaknesses and next steps should also be included.

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

# Appendix {-}

>>>>

## Analyzing Voter Preferences Across Education, Race, Gender AND Age

The analysis reveals critical insights into how education, race, gender and age influence voting behavior. Contrary to conventional wisdom and past electoral analyses, our findings indicate a divergent pattern in voting behavior among different educational groups. The shift in party allegiance among non-college voters from Republicans to Democrats and the the dominance of popularity of the Republicans with 'Some college' and 'Postgrad' education levels challenge the stereotypical narratives that educational attainment leads to an increase in support for the Democrats. This group, especially highly educated 'Postgrad' group being the second highest supporters suggest a reevaluation of Democrats' strategies to appeal to educated voters concerned with economic policies and national security. However, according to our analysis, the Republicans fail to attract voters as highest proportion of support among the four educational groups remain under 40 percent. This almost certainly predicts that Joey Biden will become the president of the United States. This coincides with the election results where Biden won 55% of the votes from the college graduates while Trump gained 43%. Our analysis of 37% of voters college degree and 37.5% of postgrad suggest are in line with the results. However, this model has failed to estimate the winning of Trump from less educated group since we estimated 39% from voters with 'some college degree' and 36.5% from voters with 'High school or less'

+ race

+ gender: American woman for the Democratic party over the last 40 years [citation].

+ age In general, younger people tend to be more liberal and as people get older they become more conservative. From our analysis, we observe a trend where ''. 36% of '18-29' group, 46% of '30-44', 50% of 45-64 group, 52% of '+65' group voted for trump respectively in the last election (washington post + add citation). We see a continuous increase in favour of Trump as people get older.

@@

From @fig-distribution-by-state, we can observe that Trump leads in mid-west of America, Montana (MT), Wyoming (WY), Mississippi (MS), Maine (ME), Missouri (MO), Kentucky (KY), and Utah (UT). Even the competing states like Louisiana (LA), New Mexico (NM), Tennessee (TN) are also mid-west part of the country, which are rural areas with low population density. This is correctly estimated since in the real world as Trump won in these states: MT, WY, MS, MA, MI, KY, UT. He also won in LA and TN, which we considered were competing states. We can go more in depth of this study with the benefit of hindsight. We estimated that the biggest victory for Trump would be Montana (MT) with just below 70%. In reality, he won by 59.6%, which is lower than we thought but still sit within our error values. The next state with the highest proportion of support for Trump was Wyoming (WY) from our model with 65%, which is close to the election poll result of 69%. We were very successful with Mississippi (MS) with an estimation of 57% and the poll result of 57.5%. Maine (ME) was another very close estimate with 52% and the poll result of 53.1%. 56.8% voted for Trump in Missouri (MO), which was slightly higher than our estimation of 51%. We estimated that only 26% of voters in Hawaii (HI) would vote for Trump with error margins of +-10%, which matched 34.3% for Trump in the election. 41.9% for Trump in Colorado (CO) lie within our estimate of 37% with +-5% margins. 
+ how blue-collar workers became dissatisfied with the democratic government (wilson)

@@

Big cities and large suburban areas along the west coast and the east coast favored Biden whereas Trump supporters are mostly in the rural areas in the mid-south and mid-north states.

Historically, the Republicans

We were able to estimate the winning of states with some success. From the data and analysis outlined above, we believe that our model suggests that Biden will win both the popular vote and the electoral votes and become the president of the United States. This was partially right in that he did win both but with a smaller margin that we had expected. In the end, he won 306 electoral votes and won 51.3% of the votes to become the 46th US president.

@@

@@

# Appendix
